% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Craig B. Ludington\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Home Address} \\ 2446 North Albany Avenue \\ Chicago, IL 60647-2602  \\
        (773) 627-2020 }
\address{{\bf Email Address} \\ me@clojure.us }

 
\begin{resume} 
 
\section{Summary} 
\begin{itemize} \itemsep -2pt % reduce space between items
\item Abstracter, simplifier, cutter of Gordian knots
\item Programmer of Clojure, Clojurescript, Ethereum, Go, Common Lisp, Ruby, C++, C, Bash and elisp (and several other languages)
\item Unix proselytizer (Linux, Solaris, HP-UX, AIX, OS X)
\item Database-proficient (PostgreSQL, Oracle, Informix, MySQL)
\item Unix shell expert
\item Emacs expert
\end{itemize}

\section{Experience}

 {\bf Developer,} A Chicago financial company \hfill Present
\begin{itemize} \itemsep -2pt % reduce space between items
\item Developed a blockchain payments system with Clojure, Clojurescript, and Ethereum smart contractsﬂ
\end{itemize}


 {\bf Developer,} Nelson Cash, Chicago, IL \hfill March 2014 - July 2015
\begin{itemize} \itemsep -2pt % reduce space between items
\item Conceived, developed, and delivered a product that was sold to a major player in the network search field. (Clojure, Clojurescript, and Go)
\item Led a team of four developers and one designer.
\item Designed and implemented copy-fitting software that generated a distinct logo for each of 28,531 US cities. (Clojure, targeting SVG)
\item Implemented the backend for a social website for advertising agencies to share case studies with clients and other agencies.  (Clojure, Appengine datastore and blobstore)
\end{itemize}

 {\bf Senior software engineer,} Enova Financial, Chicago, IL \hfill July 2008 - March 2014
\begin{itemize} \itemsep -2pt % reduce space between items
\item Clojure data storage system let us move terabytes of binary large objects out of the PostgreSQL database.
\item ActiveRecord ``Archivable'' Ruby module made the data in the Clojure system just another readable/writable attribute.
\item Completed and released large and small projects in Ruby on Rails for the company's primary public-facing web site.
\item Implemented credit models, fraud detection strategies, new product lines for the company's lending platform backend.
\end{itemize}


 {\bf Director of Technology Services,} onShore Development, Chicago, IL \hfill June 2002 - March 2007
\begin{itemize} \itemsep -2pt % reduce space between items
\item Primary product is a Common Lisp scheduling and resource lending system for higher education (especially film schools).
\item Managed programmers, quality assurance team and technical support staff.
\item Matured an existing system and created a new product line.
\item Delighted customers at over a hundred schools across the company.
\end{itemize}

 {\bf Consultant} \hfill 1996 - 2002
\begin{itemize} \itemsep -2pt % reduce space between items
\item Served clients in telecommunications, manufacturing, web services, insurance, and software as a product, or software as a service.
\end{itemize}

\section{Sample Consulting Projects}
\begin{itemize} \itemsep -2pt % reduce space between items
\item Wrote a Mail Transfer Agent (MTA) (implemented outbound mail only, could handle MAX\_FD concurrent connections).
\item Implemented a compiler for RPG, an AS/400 language we were porting to HPUX.  I wrote the lexical analyzer in C.
\item Created a library and framework for interprocess communication in a fax delivery system for UUNET. Also C.
\item Filesystem-based database system for storing telephone numbers and metadata.  It was essentially a trie data structure of directories and files.  Written in C.
\end{itemize}
\end{resume}
\end{document} 



