% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Craig B. Ludington\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Home Address} \\ 2446 North Albany Avenue \\ Chicago, IL 60647-2602  \\
        (773) 627-2020 }
\address{{\bf Email Address} \\ craig.ludington@rimpoche.chi.il.us }

 
\begin{resume} 
 
\section{Summary} 
Systems, applications, and network programming on a variety of platforms.
Strong Unix, Ruby, Common Lisp, C++ and  C background.
Excellent analytical and design skills.
Experienced in all phases of software development life-cycle.

\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & Ruby, Common Lisp, C++, C, SQL, TCL/TK, Lex, Yacc, Awk, Korn and Bourne shells, Perl, Bash, Python \\
     \underline{Operating Systems:} & Unix (Solaris, Sys V, HP-UX, OSF1, SunOS, Linux, BSDI), OS/2, DOS
 \end{tabular}


\section{Experience}
 {\bf Senior software engineer,} Enova Financial, Chicago, IL \hfill July 2008 - Present
\begin{itemize} \itemsep -2pt % reduce space between items
\item Ruby on Rails for an on-line lender's public-facing web site. 
\item Implemented credit-models, fraud detection strategies, and a new product line in an international market.
\item Specified and coded an API for third-party agents to use in selling our service to their customers.
\end{itemize}



 {\bf Director of Technology Services,} onShore Development, Chicago, IL \hfill June 2002 - March 2007
\begin{itemize} \itemsep -2pt % reduce space between items
\item Developed WebCheckout, a web-based resource scheduling and inventory management application written in Common Lisp.  
\item Created a new product, Patron Initiated Reservations.
\end{itemize}

 {\bf Title,} Company, Chicago, IL \hfill Month Year - Month Year
\begin{itemize} \itemsep -2pt % reduce space between items
\item 
\item 
\item 
\end{itemize}


\end{resume} 
\end{document} 



